### 2022-10-04 PSTAT131_Final_Project.Rmd
edit

>>>>

```{r}
pokemon %>%
  distinct(classfication)
```

Might not be a good idea to do classification because there are 588 unique classifications of a pokemon --> better to focus on type

```{r}
library(corrplot)
pokemon_numeric <- pokemon %>%
  select_if(is.numeric)
# taking out the aforementioned columns with too many missing values (was not planning on using them anyways)
pokemon_numeric <- pokemon_numeric[, !names(pokemon_numeric) %in% c("height_m", "weight_kg", "percentage_male")]

pokemon_cor <- cor(pokemon_numeric)
pokemon_corrplot <- corrplot(pokemon_cor)
```

We can see that how a pokemon performs against a certain other type of pokemon is not really correlated to capture rate much. However, this also shows how capture rate has a high negative correlation with base_total which is the Base Stat Total (BST = hp + attack + defense + sp_attack + sp_defense + speed). So, it might be worth exploring how all of those added together affects the capture rate.

```{r}
ggplot(pokemon, aes(capture_rate)) + geom_histogram()
```

No specific skewness is visible, but there is a peak in the data around 40-50 capture rate.
